Spring haul-out behavior of seals in the Bering and Chukchi seas

### 2024-04-05 analysis/paper/London_HauloutBehavior.Rmd
additional color blind friendly improvements

pal <- c(rcartocolor::carto_pal(12,'Bold')[1:11],
         rcartocolor::carto_pal(12,'Antique')[1:3])
names(pal) <- as.character(sort(unique(peak_ho_df$year)))

>>>>

# pal <- c(rcartocolor::carto_pal(12,'Bold')[1:11],
#          rcartocolor::carto_pal(12,'Antique')[1:3])
pal <- c("#A6CEE3","#3385BB","#84BF96","#6DBD57","#F3E587","#F57C7C","#E42622",
         "#FBB268","#FE8D19","#DE9E83","#9D7BBA", "#977899","#7F9D55","#B15928")
names(pal) <- as.character(sort(unique(peak_ho_df$year)))
